Supplement to: Library Learning for Neurally-Guided Bayesian Program Induction

### 2018-12-05 spotlight.tex
spotlight before Armando revisions

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{calc}
%\usetikzlibrary{arrows,shapes}
\usetikzlibrary{fit,bayesnet}

@@

\begin{minipage}[c]{0.4\textwidth}
  \begin{tikzpicture}[scale=1,line width=0.5mm]

      %% \node(f1) at ([yshift=-0.9cm,xshift=1cm]d.south) {\footnotesize progs. for task$_i$};
      %% \node(t) at ([xshift = 2cm]f1.east) (p11){\footnotesize program$_i$, task$_i$};
      %% \draw [->,squiggle ] (f1.east) -- node[above]{\footnotesize  sample} (p11.west);

%      \draw[dashed,cyan,very thick] ([yshift=0.5cm]p1.west) rectangle  ([yshift=-0.5cm,xshift=0.5cm]p11.east);

      \node(n) at ([yshift=-0.8cm,xshift=1.6cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [->,red] ([xshift=-0.4cm]n.west) to[out = -180,in = -70]  ([xshift=-0.25cm,yshift=0.1cm]p1.south);

    \end{tikzpicture}}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
  \visible<2->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
    \node at (2,1) {\underline{\textbf{Explore}: Infer programs, fixing DSL and neural net}};
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

@@

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}}

  \vspace{1cm}

\visible<3->{  \begin{tikzpicture}[scale=0.4,line width=0.5mm]

    \node at (0,0) (f1){progs. for task$_1$};
    \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
    \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

    \node(c)[rectangle, rounded corners, draw, minimum width = 3cm, minimum height = 2.5cm, anchor = north west] at (5.2,1) {};
%    \node[anchor=north] at (c.north) {Compression};
    \node at ([yshift=1cm,xshift=-5cm]c.north) {\underline{\textbf{Compress}: Update DSL, fixing programs}};
    \draw [-> ] (f1.east) -- (c.west|-f1.east);
    \draw [-> ] (f2.east) -- (c.west|-f2.east);
    \draw [-> ] (f3.east) -- (c.west|-f3.east);

@@

\begin{minipage}[c]{0.4\textwidth}
  \begin{tikzpicture}[scale=1,line width=0.5mm]

@@

      %% \node(f1) at ([yshift=-0.9cm,xshift=1cm]d.south) {\footnotesize progs. for task$_i$};
      %% \node(t) at ([xshift = 2cm]f1.east) (p11){\footnotesize program$_i$, task$_i$};
      %% \draw [->,squiggle ] (f1.east) -- node[above]{\footnotesize  sample} (p11.west);

%      \draw[dashed,cyan,very thick] ([yshift=0.5cm]p1.west) rectangle  ([yshift=-0.5cm,xshift=0.5cm]p11.east);

      \node(n) at ([yshift=-0.8cm,xshift=1.6cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [->,red] ([xshift=-0.4cm]n.west) to[out = -180,in = -70]  ([xshift=-0.25cm,yshift=0.1cm]p1.south);

    \end{tikzpicture}}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
  \visible<2->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
    \node at (2,1) {\underline{\textbf{Explore}: Infer programs, fixing DSL and neural net}};
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}}

  \vspace{1cm}

\visible<3->{  \begin{tikzpicture}[scale=0.4,line width=0.5mm]

    \node at (0,0) (f1){progs. for task$_1$};
    \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
    \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

    \node(c)[rectangle, rounded corners, draw, minimum width = 3cm, minimum height = 2.5cm, anchor = north west] at (5.2,1) {};
%    \node[anchor=north] at (c.north) {Compression};
    \node at ([yshift=1cm,xshift=-5cm]c.north) {\underline{\textbf{Compress}: Update DSL, fixing programs}};
    \draw [-> ] (f1.east) -- (c.west|-f1.east);
    \draw [-> ] (f2.east) -- (c.west|-f2.east);
    \draw [-> ] (f3.east) -- (c.west|-f3.east);

@@

@@

\end{document}

>>>>

\usepackage{amssymb,amsmath}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{calc}
%\usetikzlibrary{arrows,shapes}
\usetikzlibrary{fit,bayesnet}

@@

\begin{minipage}[c]{0.6\textwidth}
  \visible<2->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
      \node at (2,1) {\underline{\textbf{Explore}: Infer programs, fixing DSL and neural net}};
      \begin{scope}[shift = {(-3,0)}]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

@@

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
      \end{scope}
      \visible<5->{
        \node(repeat)[scale=8] at (6,-3.5) {$\circlearrowleft$};
        \node at (repeat) {\emph{Repeat!}};
      }
  \end{tikzpicture}}

  \vspace{-1.5cm}

\visible<3->{  \begin{tikzpicture}[scale=0.4,line width=0.5mm]
    \node at (0,0) (f1){progs. for task$_1$};
    \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
    \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

    \node(c)[rectangle, rounded corners, draw, minimum width = 3cm, minimum height = 2.5cm, anchor = north west] at (5.2,1) {};
%    \node[anchor=north] at (c.north) {Compression};
    \node at ([yshift=1cm,xshift=-3cm]c.north) {\underline{\textbf{Compress}: Update DSL, fixing programs}};
    \draw [-> ] (f1.east) -- (c.west|-f1.east);
    \draw [-> ] (f2.east) -- (c.west|-f2.east);
    \draw [-> ] (f3.east) -- (c.west|-f3.east);

@@

\end{minipage}%
\begin{minipage}[c]{0.28\textwidth}
  \vspace{-1cm}
  \begin{tikzpicture}[scale=1,line width=0.5mm]

@@

      \node(n) at ([yshift=-1.2cm,xshift=1.6cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [->,red] ([xshift=-0.4cm]n.west) to[out = -180,in = -70]  ([xshift=-0.25cm,yshift=0.1cm]p1.south);
%      \node at ([xshift=-0.5cm]$(p1.south)!0.5!(n.west)$) {\textbf{Loss4%}};

    \end{tikzpicture}}
\end{minipage}

@@

%% \begin{frame}{Explore/Compress/Compile as {\color{red}Amortized} Bayesian Inference}

%% \newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
%%       \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
%%       \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
%%       \node[rectangle] at (1,1) {};
%%       \foreach \name / \y in {1,...,4}
%%           \node[neuron] (I-\name) at (0,-\y) {};
%%       \foreach \name / \y in {1,...,3}
%%           \node[neuron] (H-\name) at (1,-\y-0.5) {};
%%       \foreach \name / \y in {1,...,4}
%%           \node[neuron] (O-\name) at (2,-\y) {};
%%       \foreach \source in {1,...,4}
%%           \foreach \dest in {1,...,3}
%%               \draw [-latex] (I-\source) -- (H-\dest);
%%       \foreach \source in {1,...,3}
%%           \foreach \dest in {1,...,4}
%%               \draw [-latex] (H-\source) -- (O-\dest);
%%     \end{tikzpicture}}

%% \begin{minipage}[c]{0.4\textwidth}
%%   \begin{tikzpicture}[scale=1,line width=0.5mm]

%%   \node[latent,scale=1] at (3.5,3) (dx){DSL};
%%   \node[latent,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
%%   \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
%%   \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
%%   \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
%%   \draw [->] (zp1.south) -- (xp1.north);
%%   \draw [->] (dx.south) -- (zp1.north);
%%   \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

%%   \node[latent,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
%%   \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {task};
%%   \draw [->] (zp1.south) -- (xp1.north);
%%   \draw [->] (dx.south) -- (zp1.north);
%%   \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

%%   \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
%%   \draw [->] (dx.south) -- (zp.north);
%%   \draw [->] (zp.south) -- (xp.north);

%%   \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
%%   \node at ([xshift=3.2cm]dx.east]) (uses){is};k
%%   \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.17}};
%%   \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
%%   ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
%%   \end{tikzpicture}

%% \visible<4->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
%%     \node at (0,0) {\underline{\textbf{Compile}: Train {\color{red} recognition model}}};
%%           \node[align=center] at (-3,-1) (d){DSL};
%%       %    \node at ([xshift = 3cm]d.east) (p2){program};
%%       \node at ([xshift=2.5cm,yshift = 0cm]d.east) (p1){program};

%%       \draw[squiggle,-> ] (d.east) -- node[sloped,above]{\footnotesize  sample} (p1.west);

%%       \node at ([xshift = 2.5cm]p1.east) (t1){ task};

%%       \draw [-> ] (p1.east) -- node[above]{\footnotesize  run} (t1.west);

%%       %% \node(f1) at ([yshift=-0.9cm,xshift=1cm]d.south) {\footnotesize progs. for task$_i$};
%%       %% \node(t) at ([xshift = 2cm]f1.east) (p11){\footnotesize program$_i$, task$_i$};
%%       %% \draw [->,squiggle ] (f1.east) -- node[above]{\footnotesize  sample} (p11.west);

%% %      \draw[dashed,cyan,very thick] ([yshift=0.5cm]p1.west) rectangle  ([yshift=-0.5cm,xshift=0.5cm]p11.east);

%%       \node(n) at ([yshift=-0.8cm,xshift=1.6cm]p1.south) {
%%         \NeuralNetwork{0.17}};
%%       \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
%%       \draw [->,red] ([xshift=-0.4cm]n.west) to[out = -180,in = -70]  ([xshift=-0.25cm,yshift=0.1cm]p1.south);

%%     \end{tikzpicture}}
%% \end{minipage}
%% \begin{minipage}[c]{0.55\textwidth}
%%   \visible<2->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
%%     \node at (2,1) {\underline{\textbf{Explore}: Infer programs, fixing DSL and neural net}};
%%     \node at (0,0) (d){DSL};
%%     \node at ([yshift = -2cm]d) (t){$\text{Task}$};

%%     \node at ([xshift = 2cm]t) (nn){
%%       \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.2,shift={+(-1,2.5)}}]
%%         \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
%%         \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
%%         \node[rectangle] at (1,1) {};
%%         \foreach \name / \y in {1,...,4}
%%             \node[neuron] (I-\name) at (0,-\y) {};
%%         \foreach \name / \y in {1,...,3}
%%             \node[neuron] (H-\name) at (1,-\y-0.5) {};
%%         \foreach \name / \y in {1,...,4}
%%             \node[neuron] (O-\name) at (2,-\y) {};
%%         \foreach \source in {1,...,4}
%%             \foreach \dest in {1,...,3}
%%                 \draw [-latex] (I-\source) -- (H-\dest);
%%         \foreach \source in {1,...,3}
%%             \foreach \dest in {1,...,4}
%%                 \draw [-latex] (H-\source) -- (O-\dest);
%%       \end{tikzpicture}
%%     };
%%     \node[align = center, text width = 1cm] at ([yshift = 0.9cm,xshift=-0.5cm]nn.north) {\baselineskip=0pt \small Recog. model\par};
%%     \draw [red,-{>[scale=0.2]}] (t.east) -- ([xshift = -0.5cm]nn.west);

%%     \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.2cm,yshift = -1cm]) (s){Search};

%%     \draw [red,->] ([xshift = 0.5cm]nn.east) -- ([yshift = -0.25cm]s.west);
%%     \draw [->,rounded corners,] (d.east) -- ([yshift = 2cm]nn.center) -- ([yshift = 0.25cm]s.west);

%%     \node[align=left] at ([xshift=2cm]s.east) (f) {Programs};
%%     \draw [->  ] (s.east) -- (f.west);

%%     \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
%%   \end{tikzpicture}}

%%   \vspace{1cm}

%% \visible<3->{  \begin{tikzpicture}[scale=0.4,line width=0.5mm]

%%     \node at (0,0) (f1){progs. for task$_1$};
%%     \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
%%     \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

%%     \node(c)[rectangle, rounded corners, draw, minimum width = 3cm, minimum height = 2.5cm, anchor = north west] at (5.2,1) {};
%% %    \node[anchor=north] at (c.north) {Compression};
%%     \node at ([yshift=1cm,xshift=-5cm]c.north) {\underline{\textbf{Compress}: Update DSL, fixing programs}};
%%     \draw [-> ] (f1.east) -- (c.west|-f1.east);
%%     \draw [-> ] (f2.east) -- (c.west|-f2.east);
%%     \draw [-> ] (f3.east) -- (c.west|-f3.east);

%%     \node[right](d) at ([xshift = 1.6cm,yshift = -0.0cm]c.east) {
%%       \begin{tikzpicture}[scale=0.6]
%%         \node[align=center] at (0,0) {DSL+};
%% \begin{scope}[shift={(0.6,-0.5)}]
%%   \node[pop3](p1) at (-1,-1) {\code{+}};
%%   \node[pop3](n1) at (0.6,-0.9) {\code{1}};
%%   \node[pop3](a) at (0,-1) {\code{ }};
%%   \draw[pop3] (0,0) -- (p1.north);
%%   \draw[pop3] (0,0) -- (n1.north);
%%   \draw[pop3] (-0.3,-0.3) -- (a.north);
%%   \end{scope}
%%         \end{tikzpicture}
%%       };
%%     \draw [-> ] (c.east) -- (d.west);

%%     \node at (c.center) {
%% \begin{tikzpicture}[scale=0.6]

%%   \begin{scope}[shift={(0.9,-1.3)}]
%%       \node(l1) at (0,0) {};
%%   \node[color=pop3](p1) at (-1,-1) {\code{+}};
%%   \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
%%   %\node(x1) at (0,-1) {};
%%   \draw[color=pop3] (l1.south) -- (p1.north);
%%   \draw[color=pop3] (l1.south) -- (n1.north);
%%   \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

%% %  \node [rotate=90] at (-2.3,-0.7) {\small program};

%% \end{tikzpicture}
%%     };

%%     \end{tikzpicture}}

%%   \end{minipage}

@@

\begin{frame}{\Huge Learning to program: Poster AB \#24}

\centering\includegraphics[width = \textwidth]{figures/finale.png}

  \end{frame}
\end{document}
